\chapterwithauthor{Runa Bhattacharjee}{My Project Taught Me how to Grow Up}
\chapterwithauthor{Runa Bhattacharjee}{我的事业教我怎样成长}

\authorbio{For the past 10 years, Runa Bhattacharjee has been translating and working on
localizing numerous Open Source projects - ranging from Desktop interfaces to
Operating System tools and lots of things in between. She strongly believes that
upstream repositories are the best places to submit any form of changes. She also
holds a professional portfolio specializing in Localization, at Red Hat. Runa
translates and maintains translations for Bengali (Indian version), but is
always happy to help anyone wanting to get started with localization.}
\authorbio{过去的10年中，Runa Bhattacharjee一直致力于翻译和为了区域化
众多的开源项目而工作——包括了从桌面借口到操作系统工具等很多东西。她坚信
上游库是提交任何形式的变化的最好的地方。她同时也在红帽子的专业区域里拥有一个专家职位。
Runa为孟加拉（印度版）进行翻译和维护翻译，但她通常很乐意去帮助任何一个想要开始致力于
区域化工作的人。}

\section*{Introduction}
\section*{介绍}

Burning the midnight oil has been a favorite form of rebellion by young people
all over the world. Whether to read a book with a torchlight under the covers or
to watch late night TV reruns or (amongst other things) to hang around on an IRC
channel and tinkering around with an itchy problem with a favorite open source
project. 
熬夜成了全世界的年轻人最喜爱的反叛形式。不管是在被子下面借助电筒的光看书还是
看晚间电视重播或者是（在别的事件之间）在一个IRC频道上漫无目的地观看同时鼓捣最喜欢
的开源软件令人难受的问题。

\section*{How it all began}
\section*{这是如何开始的}

That is how it all began for me. Let me first write a bit about myself. When I
got introduced to the local Linux Users Group in my city, I was in between jobs
and studying for a masters degree. Very soon I was a contributor to a few
localization projects and started translating (mostly) desktop interfaces. We
used a few customized editors with integrated writing methods and fonts. The
rendering engines had not matured well enough to display the script with zero
errors on the interfaces, nonetheless we kept on translating. My focus was on
the workflow that I had created for myself. I used to get the translatable
content from the folks who knew how things work, translate it as best as I
could, add in the comments to help the reviewers understand how I comprehended
the text, filled in the necessary information for copyright and credits and sent
them back to the coordinators.
对我来说这一切都是如何开始的。让我先写一些关于我的事情。
我被介绍进我市当地的Linux用户组的时候，我正在一边工作一边攻读硕士学位。很快我便加入了几个
区域化项目，开始翻译（主要是）桌面界面。我们用一些有综合编写模式和字体的特定编辑器进行编写。
虽然渲染引擎还没有完善到能够零错误的在界面上显示脚本，但是我们还是继续翻译。我的注意力都
放在我为我自己设计的工作流程上。我之前都是从懂得运行原理的人那里知道可译的内容，
尽我所能地翻译，同时增加注释帮助审稿人了解我对文章的理解，填写必要的版权和积分信息
并返回给协调员。

\section*{How it was done}
\section*{这是如何做的}

It was mostly a simple way of doing things. But most importantly it was
\textit{my} independent way of doing things. I took my own time to schedule when
I would work on the translations. These would then be reviewed and returned to
me for changes. Again, I would schedule them for completion as per how I could
squeeze out some time from all the studying and other work that I was doing.
When I did get down to work, I would sit through 9-10 straight hours mostly into
the wee hours of the morning, feeling a high of accomplishment until the next
assignments came through.
这是一个简单的做事情的方式。但最重要的是这是
\textit{我}自己自主的做事方式。
我把我的时间进行安排，计划好做翻译的时间。这些计划将会被审查并且反馈给
我以便做出调整。我会按照我能从我的学习或者其他所做的工作中挤出的时间，
再次调整来完成计划。当我开始工作的时候，我会在那一直做9-10个小时差不多到凌晨，
感觉很有成就感知道下一个工作通过。
\section*{What mattered}
\section*{关键是什么}

What I did not know was that I played a significant part in the larger scheme of
things. Namely, release schedules. So, when I completed my 2 cents of the task
and sent them over, I did not factor in a situation where they could be rendered
useless because they were too late for the current release and too early for the
next release (which would invariably contain a lot of changes that would require
a rework). Besides these, I was oblivious to the fact how it all mattered to the
entire release process -- integration, packaging, interface testing, bug filing,
resolution.
我不知道的是，我在更大的计划中拥有着重要的职责。也就是，发布时间表。
所以，当我完成了2%的任务就把它们提交了，我没有考虑它们变得毫无用处的情况，因为它们
对当前版本来说出现太迟了，并且对下一个版本来说太早（这将不可避免地包含了很多的变化，
需要返工）。除了这些，我忽视了这是如何关系到整个发布过程的事——整合，包装，
接口测试，错误归档，分辨率。

\section*{How it made me grow up}

All these changed drastically when I moved into a more professional role. So
suddenly I was doing the same thing but in a more structured order. I learned
that the cavalier road-rolling that I had been used to, was not scalable when
one had to juggle through 2-3 release schedules. It had to be meticulously
planned to map with the project roadmaps. While working on translating a desktop
interface, one had to check what the translation schedule was for the main
project. The projected date to start working would be right after when all the
original interface messages had been frozen. Translators could then work
unhindered until the translation deadline, after which they would be marked as
stable in the main repositories and eventually packages would be built. Along
with these schedules, a couple of operating system
distributions would align their schedules as well. So the translators had the
additional responsibility of making sure that the pre-release versions of the
operating system that would be carrying the desktop, went through with some bits
of testing to ensure that the translations made sense on the interface and did
not contain errors.

\section*{What I should have known}

The transition was not easy. Suddenly there was a flood of information that I
had to deal with and additional chores that I had to perform. From being a hobby
and more importantly a stress-buster, suddenly it was serious business. Thinking
in retrospect, I can say that it probably helped me understand the entire
process because I had to learn it from the ground up. And armed with that knowledge
I can analyze situations with a better understanding of all the effective
facets. At the time when I started working on the Open Source project(s) of my
interest, there were much fewer professionals who worked full time in this
domain. Most of the volunteer contributors held day jobs elsewhere and saw these
projects as a way to nurture the creative juices that had dried up in their
routine tasks. So a number of newcomers were never mentored about how to plan
out their projects professionally. They grew to be wonderfully skilled in what
they were doing and eventually figured out how they would like to balance their work
with the rest of the things they were doing.

\section*{Conclusion}

These days I mentor newcomers and one of the first things that I let them know
is how and in which part of the project they matter. Crafting an individual
style of work is essential as it allows a person a comfortable space to work in,
but an understanding of the organized structure that is affected by their work
imbibes the discipline that is required to hold in check chances of arbitrary
caprice.
