\chapterwithauthor{Armijn Hemel}{写了再说}

\authorbio{自从1994年，Armijn Hemel的哥哥带回家一堆装有FreeBSD早期版本的软盘，Armijn Hemel
就开始使用自由软件。一年后，他决定使用linux，并且自此以后，不论是在家里，Utrecht大学还是在工作上，
他都一直使用类UNIX操作系统。
从2005年起，Armijna成了gpl-voilations.org组织的核心团队成员，同时让他自己的咨询公司（Tjaldur Software Governance Solutions）
专注与GPL协议违规的检测和解决。
}

\noindent{}追溯到1999年，我开始参与FLOSS的行动。那时，我使用Linux和FreeBSD已经有些年份了，但是仅仅作为
使用者。我想做些实际的贡献，但是找不到合适的项目参与进去，所以我决定开始我自己的项目。回想起开始的原因，我想有很多。
一个因素是，我不确定自己的代码是否够优秀，以至于现有的项目愿意接受（我一直很平庸）。那么自己的项目里就不会有这样的情况了。
第二点也许是年轻的冲劲。

我想写个演示程序，能比PowerPoint的特性高级（可能你觉得更糟）。当时，没有OpenOffice，只能选用
LaTex或者Magicpoint。而这两者更多的为文本展示做定制，展示旋转效果就不行了。我想写跨平台的，那时觉得Java
会是最好的选择。目标是完成一个用Java写的展示程序，它支持所有的旋转特效。我构想了一下，然后开始项目。

Infrastructure-wise everything was there: there was a mailing list, there was a
website, there was source code control (CVS). But there was no actual code for
people to work on. The only things I had were some ideas of what I wanted to do,
an itch to scratch and the right buzzwords. I actually wanted people to join in
creating this program and make it a truly collaborative project.

基础设施是这样的：一个邮件列表，一个网站，一个源码版本控制库（CVS）。但是并没有实际的代码
可以让人们在上面贡献。那时我仅有的是一些我想如何做的念头，一颗骚动的心还有正确的流
行词汇。
我实际上希望人们能够加入建设这个项目，并且把它变成一个真正的合作项目。

I started making designs (with some newly acquired UML knowledge) and sent them
around. Nothing happened. I tried to get people involved, but collaboratively
working on a design is very hard (besides, it is probably not the best way to
create software in the first place). After a while I gave up and the project
silently died, without ever producing a single line of code. Every month I was
reminded by the mailing list software that the project once existed, so I asked
it to be taken offline.

我开始做了些设计（用那时新学的UML知识）并且把它们发布出去。什么都没发生。
我尝试让人们加入，但是协作设计非常困难（此外，这也不是开始阶段创建软件的最好方法）。
一段时间后，我放弃了，项目默默死去，一行代码也
没有产生。每个月，我都被邮件列表软件提醒，项目曾经存在，所以我就把邮件列表关了。

I learned a very valuable, but somewhat painful, lesson: when you announce
something and when you want people to get involved in your project, at least
make sure there is some code available. It does not have to be all finished, it
is OK if it is rough (in the beginning that is), but at least show that there is
a basis for people to work with and improve upon. Otherwise your project will go
where many many projects, including my own failed project, have gone: into
oblivion.

我学到了一堂有价值，但是有所疼痛的经验：当你宣布了一些东西，并且希望别人加入你的项目，
至少，确保已经有一些的代码了。代码不必要是完成的，可以是粗略的（开始的时候），但是至少
展现出存在了一定的基础工作，好让人们一起为之工作并且提升它。否则你的项目会和很多很
多项目一样，包括我那个失败的项目，被遗忘。


I eventually found my niche to help advance FLOSS, by making sure that the legal
underpinnings of FLOSS are tight through the gpl-violations.org project. In
retrospect I have never used, nor missed, the whirly effects in presentation
programs and found them to be increasingly irritating and distracting too much
from the content. I am happily using LaTeX beamer and occasionally (and less
happily) OpenOffice.org/LibreOffice to make presentations.

我最终找到了自己的位置。我通过确保FLOSS的法律基础是严格通过gpl-violations.org
项目的，去帮助提升FLOSS。回想起来，我从没用过，或错过，演示程序中的旋转效果。并且我发
现它们会增加争执，还会过于分散内容。我很高兴使用LaTex beamer，
或有时候（不那么高兴）使用OpenOffice.org/LibreOffice 去做演讲。


FLOSS:是Free Libre Open-Source Software的缩写，在2001年由Rishab Aiyer Ghosh提出。
（参见：http://en.wikipedia.org/wiki/Free_and_open-source_software）
