\chapterwithauthor{凯文·欧登}{大学和社区}

\authorbio{凯文·欧登是KDE社区的元老级黑客。
他对KDE平台的重大贡献，集中在API设计和框架搭建上。
2007年毕业，他得到了计算机科学方面的博士学位，这让他主要从事本体工程（ontologies engineering）和多智能体系统（multi-agent systems）的工作。
凯文在KDBA的工作包括KDE周边的研究项目。
他一直生活在图卢兹，并在他以前的大学做兼职教师。
}

\section*{引言}
自由文化社区几乎都是本志愿者所驱动的。
这些人中，大部分是在大学就加入社区的。
有这么几点站得住脚的理由，支持你从事这样有趣的冒险：
年轻，精力旺盛，有好奇心，也许还想去改变世界。
这些在志愿工作中是非常必要的。

但是同时作为一个学生，是不应该花费大量时间在自由文化社区上的。
因为确实，这些社区相当大，而且很难交流。

这里出现了个可怕的问题：自由文化社区对下一代天才贡献者的招募失败了么（因为他们拒绝主动向大学扩张）？
那是个有意义的问题，我们一直试图在社区的软件产品（也就是KDE）的环境下探索这个问题。
在此文中，我们主要讨论几个在寻找问题答案时，没有被预见，但是必须解决的方面。

\section*{与当地的大学建立联系}
真的，这要从接触学生本人开始，并且，
最好的办法仍然是去他们的大学，试着向他们展示
免费文化组织是多么热情。为此，我们与
位于Toulouse的Paul Sabatier大学建立了联系 - 更准确地说，是
被命名为IUP ISI，以软件工程为重点的课程中的一项。

IUP ISI非常重视“亲自动手”观念，比如
对学生项目做预先的计划。这个方案特别有趣的一点
是，它通过不同的促销活动，将学生在团队工作中混合。
第三年和第四年，学生合作完成
一个共同的目标，这通常会促使组成七到十名学生的团队。

本实验的第一年，我们迷上了这项计划，提出新的
主题项目，专注于在KDE社区中开发软件。
Henri Massié，研究过程中的导演，一直非常
欢迎这些想法，并且让我们的实验进行到位。对于第一
一年来说，我们被分配到了两个KDE相关的软件项目。

为了快速建立信任，我们在那年决定为学生们提供工作保证。

\begin{itemize}
  \item 让教师们在讨论的话题中建立信心：被选中的
项目与IUP ISI中教授的主题相近（这就是为什么
我们在那年专注于UML建模工具和项目管理工具）。
  \item 给老师最大的可视性：我们为他们提供了一台服务器，
在那里他们可以定期建成和远程访问用于测试的学生作品。

  \item 让学生能更容易地参与社会活动：
项目的维护者将会扮演“消费者”的角色，
这样能提高对学生的要求，并且帮助他们找到
自己在社会中生活的方式。
  \item 最后，为了让学生们继续做下去，我们引入了一门短期课程，有关于如何
深入学习qt和KDE框架。
\end{itemize}

At the time of this writing, we have been through five years of such projects.
Small adjustments to the organization have been done here and there, but most of
the ideas behind it stayed the same. Most of the changes made were the result of
more and more interest from the community willing to engage with students and
of more and more freedom given to us in the topics we could cover in our
projects.

Moreover, throughout those years the director gave us continuous support and
encouragement, effectively allocating more slots for Free Culture community
projects, proving that our integration strategy was right: building trust very
quickly is key to a relationship between a Free Culture community and a
university.

\section*{Realizing teaching is a two-way process}
During those years of building bridges between the KDE community and the IUP ISI
course of study, we ended up in teaching positions to support the students in
their project related tasks. When you have never taught a classroom
full of students, you might still have this image of yourself sitting in a
classroom a few years ago. Indeed, most teachers were students once... sometimes
not even the type of very disciplined or attentive students. You were likely
having this feeling of drinking from a firehose: a teacher entering a room,
getting in front of the students and delivering knowledge to you.

This stereotype is what most people keep in mind of their years as students and
the first time they get in a teaching situation they want to reproduce that
stereotype: coming with knowledge to deliver.

The good news is that nothing could be further from the truth than this
stereotype. The bad news is that if you try to reproduce it, you are very likely
to scare your students away and face nothing else than lack of motivation on
their side to engage with the community. The image you give of yourself is the
very first thing they will remember of the community: the first time you get in
the classroom, to them \emph{you are} the community!

Not falling into the trap of this stereotype requires you to step back a bit and to realize what teaching is really about. It is not a one way process where one
delivers knowledge to students. We came to the conclusion that it is instead a
two-way process: you get to create a symbiotic relationship with your student.
Both the students and the teacher have to leave the classroom with new
knowledge. You get to deliver your expertise of course -- but to do so efficiently
you have to adapt to the students' frame of reference all the time. It is a very
humbling work.

Realizing that fact generates quite a few changes in the way you undertake
your teaching:
\begin{itemize}
  \item You will have to understand the culture of your students. They probably
have a fairly different background from you and you will have to adapt your
discourse to them; for instance, the students we trained are all part of the so-called Y generation which exhibits fairly different traits regarding leadership, loyalty and trust than previous generations.
  \item You will have to reassess your own expertise, since you will need to
adapt your discourse to their culture. You will approach your own knowledge from
very different angles than what you are used to, which will inevitably lead you
to discoveries in fields you assumed you mastered.
  \item Finally, you will have to build skills in presenting; a teaching
position is really about getting out of your comfort zone to present your own
knowledge while keeping it interesting and entertaining to your audience. It
will make you a better presenter.
\end{itemize}

As such, you will become a better teacher. Also your goals of getting well
trained students, and having students engage with a Free Culture community will
be better fulfilled.

\section*{Conclusion}
At the end of the day why would you go through all the effort
to build trust with a university and step outside of your comfort zone by
improving your teaching? Well, it really boils down to the initial question we
tried to answer:

\emph{Do Free Culture communities fail to attract new contributors out of
universities simply because of their inaction?}

In our experience the answer is \emph{yes}. Through those five years of building
up a relationship with the IUP ISI, we retained around two students per year on
average. Some of them disappeared after a while, but some of them become very
active contributors. The other ones still keep some nostalgia of that period of
their life and keep advocating even though they do not contribute directly. And
right now we have a local KDE team which managed to efficiently organize a two
day conference for our latest release party.

Of those former students, not a single one would have engaged with KDE without
those university projects. We would have completely missed those talents.
Luckily, we have not been inactive.
